### 2019-07-25 draft.tex
Remove aTGC

%%%% Your abstract, used for the UMI abstract and in your front matter
\setabstract{%
  This thesis presents several studies of monophoton final states
  using 35.9\fbinv\ of 13\unit{TeV} proton--proton collision data collected by the CMS
  experiment at the LHC in 2016. The standard model \zinvg\ cross section is measured
  as a function of photon transverse momentum. No significant deviations from standard
  model predictions are observed.
  The results are also interpreted in the context of several new physics models.
  Limits are placed on coupling strengths of anomalous triple gauge couplings between photons and \PZ\ bosons,
  new particle masses in simplified models of dark matter,
  the suppression scale of a dark matter effective field theory model,
  and the graviton mass scale in a model of extra spatial dimensions.
}

>>>>

%%%% Your abstract, used for the UMI abstract and in your front matter
\setabstract{%
  This thesis presents several studies of monophoton final states
  using 35.9\fbinv\ of 13\unit{TeV} proton--proton collision data collected by the CMS
  experiment at the LHC in 2016. The standard model \zinvg\ cross section is measured
  as a function of photon transverse momentum. No significant deviations from standard
  model predictions are observed.
  The results are also interpreted in the context of several new physics models.
  Limits are placed on new particle masses in simplified models of dark matter,
  the suppression scale of a dark matter effective field theory model,
  and the graviton mass scale in a model of extra spatial dimensions.
}

### 2019-07-25 estimation.tex
Remove aTGC

\section{Higher-order corrections}
The largest expected SM contributions to the various signal and control regions are from three $\mathrm{V}\gamma$
processes: \zinvg, \wlng, and \zllg.
The \zinvg\ response matrix (for the cross section measurement), the SM \zinvg\ yield (for aTGC limits),
and \wlng\ and \zllg\ transfer factors (described in the next section) are modeled using MC simulations.
As with other signal and background processes estimated in MC, these samples are generated to LO in QCD by MadGraph.
These $\mathrm{V}\gamma$ processes are generated with up to two extra gluons radiated from the incoming quarks,
which form jets in the final detected event.
For the aTGC analysis, redundant \zinvg\ samples are generated to LO in QCD by Sherpa, with no additional jets.

@@

\section{Signal estimation: SM and aTGC} \label{sec:signal_extraction_SM_aTGC}
Beam halo is the only process examined in this analysis with an anisotropic $\phi$ distribution.
Figure~\ref{fig:halophi} shows the distribution of beam halo photons as a function of $\phi'$.
To constrain the beam halo normalization, the signal region is split into two parts according to $|\phi'|$.
The parts defined by $|\phi'| < 0.5$ and $|\phi'| > 0.5$ are respectively called the horizontal ($H$) and vertical ($V$) signal
regions. All other sources of events have expected yields that are isotropic in $\phi$, and therefore
are expected to fall into the two signal regions in direct proportion to the $\phi$ coverage of those regions.
The fraction of the total $\phi$ span covered by signal region $S$ is denoted by $C_{S}$ ($S \in \{H,V\}$).

@@

Using the above definitions for $C_{S}$, $r_{i}$, $\nZg[j,i]$, $h$, and $\nhalo[,j]$,
the total reconstructed event yield \nS\ in each signal region (excluding aTGC contributions) is estimated according to
\begin{equation}
  \nS[,j] = C_{S} (\Sigma_{i}r_{i}\nZg[j,i] + \nWg[j] + b_{j}) + h\nhalo[,j],
\end{equation}
where $\nWg[j]$ is the total contribution of \wlng\ events to reco bin $j$, and $b_{j}$ is the total contribution to reco bin $j$ from
electron and hadron misidentification, ECAL spikes, and other minor SM background processes, in both signal regions combined.

@@

For aTGC limit setting, the values of $r_{i}$ are all fixed to their initial value of 1.0.
In this case, an additional term $C_{S} \mu s_{j}$ is added to $\nS[,j]$,
in which $s_{j}$ is the contribution from the aTGC signal to reco bin $j$ (of both signal regions combined),
and $\mu$ is a constant that represents the overall aTGC signal strength:
\begin{equation}
  \nS[,j] = C_{S} (\mu s_{j} + \Sigma_{i}r_{i}\nZg[j,i] + \nWg[j] + b_{j}) + h\nhalo[,j].
\end{equation}

>>>>

\section{Higher-order corrections}
The largest expected SM contributions to the various signal and control regions are from three $\mathrm{V}\gamma$
processes: \zinvg, \wlng, and \zllg.
The \zinvg\ response matrix (for the cross section measurement), the SM \zinvg\ prefit yield,
and \wlng\ and \zllg\ transfer factors (described in the next section) are modeled using MC simulations.
As with other signal and background processes estimated in MC, these samples are generated to LO in QCD by MadGraph.
These $\mathrm{V}\gamma$ processes are generated with up to two extra gluons radiated from the incoming quarks,
which form jets in the final detected event.

@@

\section{Signal estimation: SM} \label{sec:signal_extraction_SM}
Beam halo is the only process examined in this analysis with an anisotropic $\phi$ distribution.
Figure~\ref{fig:halophi} shows the distribution of beam halo photons as a function of $\phi'$.
To constrain the beam halo normalization, the signal region is split into two parts according to $|\phi'|$.
The parts defined by $|\phi'| < 0.5$ and $|\phi'| > 0.5$ are respectively called the horizontal ($H$) and vertical ($V$) signal
regions. All other sources of events have expected yields that are isotropic in $\phi$, and therefore
are expected to fall into the two signal regions in direct proportion to the $\phi$ coverage of those regions.
The fraction of the total $\phi$ span covered by signal region $S$ is denoted by $C_{S}$ ($S \in \{H,V\}$).

@@

Using the above definitions for $C_{S}$, $r_{i}$, $\nZg[j,i]$, $h$, and $\nhalo[,j]$,
the total reconstructed event yield \nS\ in each signal region is estimated according to
\begin{equation}
  \nS[,j] = C_{S} (\Sigma_{i}r_{i}\nZg[j,i] + \nWg[j] + b_{j}) + h\nhalo[,j],
\end{equation}
where $\nWg[j]$ is the total contribution of \wlng\ events to reco bin $j$, and $b_{j}$ is the total contribution to reco bin $j$ from
electron and hadron misidentification, ECAL spikes, and other minor SM background processes, in both signal regions combined.

@@
